Discovering Focused Microgenre Communities

### 2023-08-05 main.tex

\begin{figure}[t!]
     \begin{subfigure}[b]{0.45\textwidth}
        \centering    
        \includegraphics[width=1.0\textwidth]{Plots/Micro/micro-by-age-metal.png}
        \caption{}
        \label{fig:age-metal}
    \end{subfigure}
     \begin{subfigure}[b]{0.45\textwidth}
        \centering    
        \includegraphics[width=1.0\textwidth]{Plots/Micro/micro-by-age-salsa.png}
        \caption{}
        \label{fig:age-latin}
    \end{subfigure}
\end{figure}

@@

\subsection{Salsa}
The Salsa music genre has not had as storied a career in the sociology of taste as Metal. In fact, it has been under-researched and, for the most part, ignored. I include it in the following analysis due to a shining exception to this pattern, represented in a high-quality recent study by \citep{Bachmayer2014-pk} which strongly suggests internal microgenre differentiation within this broad macrogenre label relevant to the reception and consumption side. These differentiations are keyed to hierarchical distinctions across Salsa microgenres based on social status and the concomitant internalization of class-based aesthetic dispositions \citep{lizardo2012reconceptualizing}.

@@

\subsubsection{Salsa Microgenre Analysis}
Table~\ref{tab:reg-latin} shows the result of a regression analysis analogous to that I specified for the Metal microgenres. The first column shows a model predicting choosing the ``Latin/Spanish/Salsa" macrogenre label using the usual socio-demographic covariates. The next three columns show the predictors of choosing each microgenre variation extracted from cutting the macrogenre label branch of the dendrogram at the required height. Looking at the first column, we would have concluded that choosing Salsa is not predicted by either respondent's ($p = 0.26$) or parent's ($0.17$) education, suggesting that taste for this genre is orthogonal to cultural capital and status. Instead, Salsa is mainly a genre preferred by young respondents (negative linear effect of age) who identify as Hispanic (no surprise there) and as women ($p < 0.05$).

@@

I proposed to do this using recent developments in the discovery of \textit{overlapping communities} in networks \citep{ahn_etal10}, which partially answers two of the challenges of macrogenre critics: The fact that actual genres are overlapping and not crisply bounded. The fact that there is hidden heterogeneity within the broad labels we usually focus on. Our analysis contrasted the application of the usual techniques to the same data, conceived in the usual ``macro" way, and \textit{after} upping the relationality and discovering the microgenres hidden within. Focusing on microgenres reveals variations and patterns of cultural choice (as well as audience segmentation) that we would not have noticed using the standard approach (in this, the critics are right). Still, we could do this without dropping the label or querying people about hundreds of micro-styles (most of which they'd be unfamiliar with). Instead, we exploited the venerable principle, etched into classical approaches to defining genres in network terms \citep{dimaggio1987classification}, noting that if genres are defined by the people who choose them, then they are also defined by the other choices that people make when they choose them; the country that combines with one version of Classical may not be the same country that combines with a version of the Blues (and neither is the same as the country that refuses to combine with any other style).

>>>>

\begin{figure}[t!]
     \begin{subfigure}[b]{0.45\textwidth}
        \centering    
        \includegraphics[width=1.0\textwidth]{Plots/Micro/micro-by-age-metal.png}
        \caption{}
        \label{fig:age-metal}
    \end{subfigure}
     \begin{subfigure}[b]{0.45\textwidth}
        \centering    
        \includegraphics[width=1.0\textwidth]{Plots/Micro/micro-by-age-salsa.png}
        \caption{}
        \label{fig:age-salsa}
    \end{subfigure}
\end{figure}

@@

\subsection{Salsa}
The Salsa music genre has not had as storied a career in the sociology of taste as Metal. In fact, it has been under-researched and, for the most part, ignored. I include it in the following analysis due to a shining exception to this pattern, represented by a qualitative study by \citet{Bachmayer2014-pk}, which strongly suggests internal microgenre differentiation within this broad macrogenre label relevant to the reception and consumption side. These differentiations are keyed to hierarchical distinctions across Salsa microgenres based on social status and the concomitant internalization of class-based aesthetic dispositions \citep{lizardo2012reconceptualizing}.

@@

\subsubsection{Salsa Microgenre Analysis}
Table~\ref{tab:reg-latin} shows the result of a regression analysis analogous to that I specified for the Metal microgenres. The first column shows a model predicting choosing the ``Latin/Spanish/Salsa" macrogenre label using the usual socio-demographic covariates. The next three columns show the predictors of choosing each microgenre variation extracted from cutting the macrogenre label branch of the dendrogram at the required height. Looking at the first column, we would have concluded that choosing Salsa is not predicted by either respondent's ($p = 0.26$) or parent's ($p = 0.17$) education, suggesting that taste for this genre is orthogonal to cultural capital and status. Instead, Salsa is mainly a genre preferred by young respondents (negative linear effect of age) who identify as Hispanic (no surprise there) and as women ($p < 0.05$).

@@

I proposed to do this using recent developments in the discovery of \textit{overlapping communities} in networks \citep{ahn_etal10}, which partially answers two of the challenges of macrogenre critics: The fact that actual genres are overlapping and not crisply bounded, and the fact that there is hidden heterogeneity within the broad labels we usually focus on. Our analysis contrasted the application of the usual techniques to the same data, conceived in the usual ``macro" way, and \textit{after} upping the relationality and discovering the microgenres hidden within. Focusing on microgenres reveals variations and patterns of cultural choice (as well as audience segmentation) that we would not have noticed using the standard approach (in this, the critics are right). Still, we could do this without dropping the label or querying people about hundreds of micro-styles (most of which they'd be unfamiliar with). Instead, we exploited the venerable principle, etched into classical approaches to defining genres in network terms \citep{dimaggio1987classification}, noting that if genres are defined by the people who choose them, then they are also defined by the other choices that people make when they choose them; the country that combines with one version of Classical may not be the same country that combines with a version of the Blues (and neither is the same as the country that refuses to combine with any other style).
